Molecular dynamics simulation of synchronization in driven particles

### 2021-01-20 manuscript/manuscript_ajp_2020.tex
small changes to integration exercise

  \item {\bf Integration Methods}
    \label{ex:euler}
    Our equation of motion provides
  a direct calculation for particle velocity.
  To calculate the position of the particle we
  integrate the equation of motion using
  the standard definition of velocity
  $\vec{v}_i = d\vec{r}_i/dt$ 
  via the 
  %In our model we use the
  Euler method. % to solve this equation.
  Generally when solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  Apply the Euler method to our equation
  of motion to solve for the position of a particle
  $y_n$ at the $nth$ timestep.

  {\it invite/guide students to play with the timestep and study the results}
  %FOLLOW UP WITH THIS!
  %Because we are performing molecular dynamics
  %for a single particle on a smooth potential energy landscape,
  %we use a large simulation time step of 
  %$\Delta t = 0.01$.
  %In Sec.~\ref{sec:sync},
  %we decrease the time step
  %to treat multiple particle interactions.

@@

      \bibitem{Newman} M. Newman, Computational Physics...

>>>>

  \item {\bf Integration Methods}
    \label{ex:euler}
    To calculate the position of the particle we
    integrate the equation of motion using
    the standard definition of velocity
    $\vec{v}_i = d\vec{r}_i/dt$ 
    via the 
    %In our model we use the
    Euler method. % to solve this equation.
    Our equation of motion provides
    a direct calculation for particle velocity.
    %
  When solving ordinary differential equations,
  the Euler method is effective for solving linear equations
  of the form
  $dy/dt = f(t,y(t))$ with initial condition $y(t_0) = y_0$.
  The solution is calculated algorithmically
  by stepping in time through $n$ integer steps
  $t_n = t_0 + n \Delta t$.
  At each subsequent step the new
  value for $y$ is calculated as a map solution using
  discrete times 
  $y_{n+1} = y_n + f(t_n,y_n)$.
  The Euler method can be applied to non-linear
  equations effectively if the time step $\Delta t$
  is kept sufficiently small \cite{Newman}.
  Apply the Euler method to our equation
  of motion to solve for the analytic expression
  of position of a particle
  $y_n$ at the $nth$ timestep (i.e. Eq.~\ref{eq:euler}).

  In our simulations we use the timestep $\Delta t = 0.001$,
  examine Fig.~\ref{fig:0}
  for timesteps $\Delta t = 0.01$ and $\Delta t = 0.1$
  over the same maximum time
  (i.e. decrease the overall simulation time).
  How to the motions of the particle compare when the timestep
  becomes large?

  %FOLLOW UP WITH THIS!
  %Because we are performing molecular dynamics
  %for a single particle on a smooth potential energy landscape,
  %we use a large simulation time step of 
  %$\Delta t = 0.01$.
  %In Sec.~\ref{sec:sync},
  %we decrease the time step
  %to treat multiple particle interactions.

@@

      \bibitem{Newman} M. Newman, Computational Physics, CreateSpace Independent Publishing Platform. (2012).
